Variable Selection

### 2015-06-30 var_select.rmd
checked var importance of vars with high NA
wrote a function

@@

```{r, echo=FALSE}
all7b<- read.csv('all7b.csv')

@@

save(all.cfor2,file= 'C:/Users/n9232371/Documents/github/consult/object/all_cfor2.RData')
load('C:/Users/n9232371/Documents/github/consult/object/all_cfor2.RData')

@@

#merge client.age column of details to all7b by code.client
all7b<- merge(all7b, details %>% select(code, client.age), by.x = 'code.client', by.y = 'code', all.x=TRUE, all.y=FALSE)

@@

* code.client
* Post.Code
* Billing.Type
* Job.Source
* Job.Detail.Primary
* Job.Detail.Secondary
* Job.Type.Primary
* Job.Type.Secondary
* Type
* Project.Value
* no.employees
* client age????
* contact.count
* JD.Primary
* JD.Second
* dist
* code.contact
* client.age

@@

>>>>

#redo client.count and contact.count according to this reduced dataset!!
client.count<- ddply(all7b, .(code.client), nrow)
all7b<- merge(all7b, client.count, by='code.client', all.x=TRUE)
all7b %>% select(code.client, client.count, V1) %>% slice(1000:1020)
all7b<- transform(all7b, diff= client.count - V1)
# all7b %>% select(code.client, client.count, V1, diff) %>% unique %>% arrange(-diff) %>% head
#above line tells us that our most popular clients are also the ones with the most lost jobs - fine
all7b$client.count<- all7b$V1
all7b<- all7b %>% select(-diff, -V1)

@@

```{r, echo=FALSE}
all7b<- read.csv('all7b.csv')[,-1]

@@

save(all.cfor2,file= 'C:/Users/n9232371/Documents/Consultbusiness/data/objects/all_cfor2.RData')
# load('C:/Users/n9232371/Documents/github/consult/object/all_cfor2.RData')

@@

#merge client.age column of details to all7b by code.client
all7b<- merge(all7b, details %>% select(code, client.age), by.x = 'code.client', by.y = 'code', all.x=TRUE, all.y=FALSE)
write.csv(all7b, 'all7c.csv')
all7c<- read.csv('all7c.csv')[,-1]

@@

* code.client
* Post.Code
* Billing.Type
* Job.Source
* Job.Detail.Primary
* Job.Detail.Secondary
* Job.Type.Primary
* Job.Type.Secondary
* Type
* Project.Value
* no.employees
* client.age
* contact.count
* JD.Primary
* JD.Second
* dist
* code.contact
* client.age

@@

```{r eliminate sme variables, echo=FALSe}
#between Job.Detail.Primary, Job.Detail.Secondary, Job.Type.Primary, Job.Type.Secondary, Type, JD.Primary, JD.Second
# need to delete some

#Job.Detail.Primary - 1A, 1B, 1C and so on. 1215 NA values - delete
#JD.Primary - 1A, 1B, 1C and so on. 628 NA values
#Job.Detail.Secondary - 1A, 1B, 1C and so on. 2090 NA values - most don't make sense (ARch housing with industrial buidling) 
#                                                            - industrial bldg with land subdivision - checked out, all wrong!
#        - some do ie 2C Sustainable design with 2B water-sensitive urban design (WSUD) - use!
#        - some do  ie 3C integrated water management and WSUD and 4C alternative sources of water supply - use!

#Job.Type.Primary - eg 1. Building Structures, 628 NA values, quite useful - guessing that it matches JD.Primary NA values

#Job.Type.Secondary - confusing
#                   - 2. LandInfrastucture could be copied into land subdivision for Job.Detail.Secondary
all7c$Job.Detail.Secondary <- as.character(all7c$Job.Detail.Secondary)
all7c$Job.Detail.Secondary<- ifelse(all7c$Job.Detail.Secondary=='2E Land Subdivision' & all7c$Job.Type.Secondary=='2. LandInfrastructure',
                                    '2. LandInfrastructure', all7c$Job.Detail.Secondary)
all7c$Job.Detail.Secondary<- ifelse(is.na(all7c$Job.Detail.Secondary) & all7c$Job.Type.Secondary=='2. LandInfrastructure',
                                    '2. LandInfrastructure', all7c$Job.Detail.Secondary)
all7c$Job.Detail.Secondary <- as.factor(all7c$Job.Detail.Secondary)

#                   - copy '4. Integrated water management' as 'water management' into JD.Second
all7c$JD.Second <- as.character(all7c$JD.Second)
all7c$JD.Second<- ifelse(is.na(all7c$JD.Second) & all7c$Job.Type.Secondary=='4. IntegratedWaterManagement',
                                    'water management', all7c$JD.Second)
all7c$JD.Second <- as.factor(all7c$JD.Second)

# Type - short description - quite good - 1206 NA's - all 2010 or earlier

#JD.Second - more detailed version of JD.Primary- 1277 NA's - across all years - keep

all7c<- all7c %>% select(-Job.Detail.Primary, -Job.Type.Secondary)

write.csv(all7c, 'all7c.csv')
all7c<- read.csv('all7c.csv')[,-1]

now left with

* code.client
* Post.Code
* Billing.Type
* Job.Source
* Job.Detail.Secondary
* Job.Type.Primary
* Type
* Project.Value
* no.employees
* client.age
* contact.count
* JD.Primary
* JD.Second
* dist
* code.contact
* client.age

Do any of these have significantly overlapping NA values???

First need to change code.client and code.contact. Need to assign NA to any code.client or code.contact with less than 3 counts

```{r NA into code.client, echo=FALSE}

#all code.clients with counts less than 3 shall be 'NA'
client.check<- ddply(all7c,.(code.client), nrow)
all7c<- merge(all7c, client.check, by='code.client', all.x=TRUE)
all7c$code.client<- as.character(all7c$code.client)
all7c$code.client<- ifelse(all7c$V1>2, all7c$code.client, NA)
all7c$code.client<- as.factor(all7c$code.client)
all7c<- all7c %>% select(-V1)

#all code.contacts with counts less than 3 shall be 'NA'
#code for 'unknown' which should be NA
all7c[all7c$code.contact %in% 'CN1983',]$code.contact <- NA
contact.check<- ddply(all7c,.(code.contact), nrow)
contact.check<- contact.check %>% filter(V1>2)
all7c$code.contact<- as.character(all7c$code.contact)
all7c$code.contact<- ifelse(all7c$code.contact %in% contact.check$code.contact, all7c$code.contact,
                            NA)
all7c$code.contact<- as.factor(all7c$code.contact)

#redo contact.count
cont.count<- ddply(all7c,.(code.contact), nrow)
cont.count[is.na(cont.count$code.contact),]$V1<- NA
all7c<- merge(all7c, cont.count, by='code.contact', all.x=TRUE)
all7c$contact.count<- all7c$V1
all7c<- all7c %>% select(-V1)

#Project.Value - anything with '0' should be 'NA'
all7c[all7c$Project.Value == 0,]$Project.Value<- NA
#check out what the ratios of inv.mlsto/Project.Value are
temp<- all7c %>% select(Project.Value, inv.mlsto,mlsto) %>% filter(!is.na(Project.Value))
temp<- transform(temp, ratio = round(inv.mlsto/Project.Value*100,2))
temp<- temp %>% filter(ratio< 16)
all7c$Project.Value<- ifelse(all7c$mlsto %in% temp$mlsto, all7c$Project.Value, NA)
write.csv(all7c, 'all7c.csv')

```{r NA overlap, echo=FALSE}

#overlapping NA values for variables with many NA's
# first lets look at Job.Detail.Secondary, Job.Type.Primary, Type, JD.Primary, JD.Second
experiment<- all7c
experiment<- experiment %>% select(code.client, Post.Code, Billing.Type, Job.Source, Job.Detail.Secondary, Job.Type.Primary, Type, Project.Value,
                                   no.employees, client.age, contact.count, JD.Primary, JD.Second, dist, code.contact, client.age)
experiment<- sapply(experiment, function(x) is.na(x))
NA.plot<- melt(experiment)
NA.plot$mlsto<- rep(all7c$mlsto, ncol(experiment))
#reorder levels for ggplot by total number of NA TRUE
# table(NA.plot$Var2, NA.plot$value)[,'TRUE']
NA.plot <- within(NA.plot, 
                         Var2 <- factor(Var2, 
                                               levels=names(sort(table(NA.plot$Var2, NA.plot$value)[,'TRUE'], 
                                                                 decreasing=FALSE))))

ggplot(NA.plot, aes(x=Var2, y=mlsto)) +
        geom_tile(aes(fill = value)) + 
        theme(axis.text.x=element_text(angle=45,hjust=1))

Yes,

* dist and Post.Code
* Job.Type.Primary and JD.Primary
* code.contact and contact.count

For now, we will treat the rest as having 'different

Run 12 cforests with the core variables!!

```{r cforests for NAs, echo=FALSE}

#function to create a subset dataframe based on extra variable
#then runs cforest, and saves variable importance ggplot in a folder

vars<- list('Job.Source', 'Job.Detail.Secondary', 'Type', 'Project.Value', 'no.employees','code.client'
            'client.age', 'contact.count', 'JD.Second', 'client.age', 'Billing.Type', c('dist','Post.Code'),
            c('code.contact','contact.count'), c('Job.Type.Primary','JD.Primary'))
cfor.plotsave<- function(extra= vars){
        for(i in 1:length(vars)){

                core.var= all7c[,names(all7c) %in% c('inv.mlsto', 'timespan', 'no.users', 
                                                     'Discipline', 'pc.pro', 
                        'client.totinv', 'client.numinv','pc.director', 'code.director', 'Num.disc', 
                        'Business', 'Biz.type', 'return.pdol', extra[[i]])]
                core.var = core.var[!is.na(core.var[,extra[[i]][1]]),]

                #run cforest
                cfor.var1= cforest(return.pdol~.,
                                   data= core.var)
                #calculate variable importances
                var.imp= varimp(cfor.var1) %>% as.data.frame
                colnames(var.imp)[names(var.imp) %in% '.']= 'imp'
                var.imp$var = rownames(var.imp)
                #reorder levels for bar plot
                var.imp<- within(var.imp, 
                    var <- factor(var,levels=var.imp[order(-abs(var.imp$imp)),]$var))

                q= ggplot(data=var.imp, aes(x=var, y=imp)) + theme(axis.text.x=element_text(angle=45,hjust=1))
                r=q + geom_bar(stat='identity') + 
                        labs(title = extra[[i]])
                #save plot
                ggsave(plot=r,
                       filename=paste('var',i,'.png',sep=''),
                       path= 'C:/Users/n9232371/Documents/Consultbusiness/barplots/cforests/')

cfor.plotsave(extra=vars)
